% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% | - Conclusions
% TEMP
% __|
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \textbf{Points our results address that are raised in the intro:}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% | - PARAGRAPH HEADER
% Conclusions on AL and results
% __|
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% | - PARAGRAPH BODY
%
% \textbf{Generation of structurally diverse search space and efficient sampling of it.}
We have described a cogent procedure for generating and searching a structurally diverse candidate space of bulk structural prototypes with a desired composition.
%
Once this space is enumerated, we show how it can can be efficiently searched using an algorithm with an active learning loop without a prior knowledge of accurate atomic positions.
%
In most cases, the DFT optimization of only a fraction of the candidates leads to identification of the most stable polymorphs.
%
In particular, this approach is well-suited for discovery in structurally diverse structures, such as metal oxides and other metal-ligand bulk systems, where there exits a large degree of structural diversity.
%
The current dataset includes octahedral, tetrahedral, square-pyramidal, cubic, and square-planar Ir-O conformers.
%
We also note, that our AL algorithm is capable of discovering experimentally known phases such as pyrite, columbite and layered \IrOtwo and several recently discovered layered \IrOthree phases formed by Li$^+$ deintercalation.
%
In particular, we have identified a number of previously unknown \IrOthree polymorphs below the metastability limit, including a new globally stable \aIrOthree phase.
%
This high valency Ir$^{6+}$ phase is stable under OER relevant conditions and has an ideal 100\% corner-sharing octahedral structure, a short Ir-O bond length of 1.93 \angstrom, and also has a very high surface coverage of active oxygens.
%
Calculations of surface thermodynamics reveal this structure and other OER stable \IrOthree phases have much higher theoretical OER activity than a benchmark rutile \IrOtwo.
%
The thermodynamic stability and high OER activity of the \aIrOthree phase may provide clues as to the nature of the yet uncharacterized structures reported after reconstruction of \ce{SrIrO_{3}} and \IrOx precursors under OER reaction conditions.
%
Methods combining diverse structural generation, AL-enabled accelerated searches, and \mbox{ab-initio} simulation of material performance could open up new avenues for in silico material design with application tailored structural properties.
% __|
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%







% | - __old__

% In conclusion, we have demonstrated an active learning accelerated algorithm for the discovery of stable crystal polymorphs by searching through a candidate space of structurally distinct iridium-oxide phases.
% %
% % TODO Can I generalize this result for both IrO2 and IrO3?
% % TODO Use percentage of total systems instead of just # of DFT calcs
% The algorithm can identify a majority of the most stable polymorphs (7 of the 10 most stable) in a candidate set after only computing a fraction of them via DFT (\mytilde90 DFT optimizations).
% %
% For \IrOtwo, we find confirm the rutile phase as the most stable crystal structure, while also finding several well known phases, including anatase, columbite, as well as several new phases of \IrOtwo.
% %
% For the relatively unexplored \IrOthree we found a new globally stable phase (\aIrOthree), a completely corner sharing octahedral structure with space group 182.
% %
% % Implications for for future studies of polymorphs
% %
% % Describe the level of acceleration achieved, effect of structural drift, implications for future studies
% We have analyzed the local and global structural coordination and revealed that octahedral coordination environments are predominantly preferred, although we also have a large degree of structural diversity in our dataset (octahedral, tetrahedral, square-pyramidal, cubic, and square-planar are all represented)
% %
% % Discuss the differences connectivity/M-O bonds lengths is different between IrO2 and IrO3
% %
% We constructed a revised bulk Pourbaix diagram for Ir-H$_2$O, including the newly found \aIrOthree phase and revealed that \aIrOthree has a substantial window of stability in the OER relevant potentials and pH.


% __|
